\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 learning.tex
.

In statistics, parametric regression is the problem of finding the
paremters of a function or \textit{predictor}, which can `best'
summarize the relationship between the given set of observed input
$\x$ and output $\x'$ vectors. The model or the kernel for the
predictor is fixed beforehand and the paramters are searched for.  The
notion of `best' is formally captured using a loss function which can
be non-linear. We use the commonly used loss function \textit{ordinary
least squares} (OLS) to fit affine and polynomial kernels of fixed degree.
~\footnote{The choice of loss function and regression analysis affects the quality of
the learnt models. As the procss of selecting an appropriate heuristic
is not straightforward, we just use the simplest one.}

If $N>n$, which is the case in the current context of \textit{finding
the best fit}, the problem is over-determined: there are more
equations than unknowns. Hence, a single set of parameters cannot be
found which fits all the data. Instead, we need to find the `best'
choice. This choice is formally defined using a loss function. For the
case of simple linear regression or OLS, the loss function is the sum
of squares of the errors in prediction.  The task is then to determine
$A$ and $B$, such that the least square error of the affine predictor
is minimized for the given data set.

>>>>

In statistics, parametric regression is the problem of finding the
paremters of a function or \textit{predictor}, which can `best'
summarize the relationship between the given set of observed input
$\x$ and output $\x'$ vectors. The model or the kernel for the
predictor is fixed beforehand and the paramters are searched for.  The
notion of `best' is formally captured using a loss function which can
be non-linear. We use the commonly used loss function \textit{ordinary
least squares} (OLS) to fit affine and polynomial kernels of fixed
degree.  ~\footnote{The choice of loss function and regression
analysis affects the quality of the learnt models. As the procss of
selecting an appropriate heuristic is not straightforward, we just use
the simplest one.} OLS defines its loss function as the sum of squares
of the errors in prediction. The task is then to determine the
parameters, such that the least square error of the predictor is
minimized for the given data set.
